---
title: "How to Use the `linreg` Package"
author: "Mir ABdul Rehman & Thor Wahlestedt"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how_to_use_linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

# Load the package or load it from the current directory
if (!requireNamespace("LinearRegressionPackage", quietly = TRUE)) {
  devtools::load_all(".")  # Load package from current directory
} else {
  library(LinearRegressionPackage)  # Load the installed package
  }
```

# **Introduction**

The linreg package provides an implementation of Ordinary Least Squares (OLS) linear regression using a reference class object. This vignette will guide you through how to use the linreg class, fit a linear model, and use its associated methods for extracting results such as coefficients, residuals, predictions, and diagnostic plots.

We'll use the famous iris dataset for examples in this vignette.

# Creating and Fitting a Linear Regression Model

To create a linear regression model, you can instantiate the linreg class by passing a formula and a dataset. For example, we will fit a model that predicts Petal.Length based on Sepal.Width and Sepal.Length using the iris dataset.

```{r}
data(iris)

# Create and fit the linear regression model
linreg_mod <- linreg$new(formula = Petal.Length ~ Sepal.Width + Sepal.Length, data = iris)
```

# Viewing Model Coefficients

After fitting the model, you can view the coefficients by using the `coef()` method. This will display the intercept and the coefficients for each predictor variable as a named vector.

```{r}
coefficients <- linreg_mod$coef()
print(coefficients)
```

# Generating Predictions

The `pred()` method returns the fitted (predicted) values for the linear model. You can use it to see the predicted values for the data used in the model.

```{r}
predictions <- linreg_mod$pred()
head(predictions)
```

# Viewing Residuals

You can access the residuals of the model using the `resid()` method. Residuals represent the differences between the actual and predicted values.

```{r}
residuals <- linreg_mod$resid()
head(residuals)
```

# Viewing Model Summary

The `summary()` method provides a detailed summary of the model, including estimates for each coefficient, standard errors, t-values, p-values, and significance levels.

```{r}
linreg_mod$summary()
```

# Plotting Residuals and Diagnostic Plots

To visually inspect how well the model fits the data, you can plot the residuals against the fitted values and generate additional diagnostic plots, such as the Scale-Location plot, using the `plot()` method.

```{r}
linreg_mod$plot()
```

# Conclusion

This vignette provided an overview of the key functionalities of the linreg package, including creating and fitting a linear regression model, viewing model coefficients, generating predictions, accessing residuals, viewing a detailed model summary, and plotting residual diagnostics. The linreg package aims to provide a simple yet comprehensive implementation of linear regression using OLS.
